---
title: "Project Euler"
author: "Aiden McCall"
date: '2023-01-14'
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Problem Solutions

These are my solutions to Project Euler questions; the answers are not intended to be the most efficient solutions possible and more so programming practise. I will be trying to stick to the outlined 'rules', specifically the 'one-minute rule' that your program cannot take longer than one minute to run.

If you are hoping to solve any of these problems, I would urge you to not look at the solutions and use the opportunity to develop problem solving skills both inside and outside any programming language.

## Problem 1

```{r Problem_1}
problem_1 <- function (number){
  # Starts a counter
  sum.count <- 0
  # Loops for the input (user defined)
  for (i in 1:number){
    # If i modulo 3 is 0 then divisible by 3.
    if (i %% 3 == 0){
      sum.count = sum.count + i
    }
    # If i modulo 5 is 0 then divisible by 5.
    else if (i %% 5 == 0){
      sum.count = sum.count + i
    }
    # Just returns the same sum.
    else sum.count = sum.count
  }
  # Prints the sum answer to console.
  sum.count
}

# Answer
problem_1(999)
```

## Problem 2

```{r Problem_2}
problem_2 <- function(n){
 fib <- vector()
 fib_count <- vector()
 fib[1] <- 1
 fib[2] <- 2
 i = 2
 sum = 0
 while (fib[i] < n){
   i = i + 1
   fib[i] = fib[i-1] + fib[i-2]
 }
 # The loop will still run the last value.
 fib <- fib[1:(length(fib) - 1)]
 for (i in 1:length(fib)){
   if (fib[i] %% 2 == 0){
     sum = sum + fib[i] 
   }
 }
 sum
}

# Solution for 4 million
problem_2(4000000)
